---
title: "Izar Code"
author: "Izar"
date: "1 5 2021"
output: html_document
---


#Loading Data and Packages

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
#loading data into Raw_Data dataframe
Raw_Data<- read.table("c://Data_Analysis//RDeeP_A549_NS.csv", header=TRUE, row.names=1, sep = ";")
```




#Normalization 

*works
Normalizing Protein data x/ntot   ##results in Norm_Data_df
```{r}
#generates 
T_P_S_df <- data.frame(Total_Protein_Sum)
T_P_S_vec <-c(T_P_S_df[1,],T_P_S_df[4,],T_P_S_df[2,],T_P_S_df[5,],T_P_S_df[3,],T_P_S_df[6,])
T_P_S_vec_div_func <- function(x){
  x/T_P_S_vec
}
Norm_Data_df <- t(data.frame(apply(Raw_Data,1,T_P_S_vec_div_func)))


```

*works----Creating seperate RNAse and Ctrl dfs    ##results in norm_RNAse & norm_Ctrl
```{r}
# Normailized RNAse only
RNAse_select_vec <- c(seq(from =2, to = 150, by = 2))
norm_RNAse <-data.frame(Norm_Data_df[,RNAse_select_vec])

#Normalized Ctrl only
Ctrl_select_vec <- seq(from =1, to = 150, by = 2)
norm_Ctrl <- data.frame(Norm_Data_df[,Ctrl_select_vec])
```

#Cleaning Data with mean and median methods
*works----
Creating df with median method ##results in 3680 RNAse_median_df & Ctrl_median_df
Wird angenommen, dass der Median eine gute Methode für n=3 stichproben ist, die robust gegenüber OUtlieren ist."https://wis.kuleuven.be/statdatascience/robust/papers/2002/rousseeuwverboven-robustestimationinverysmallsampl.pdf"
```{r}
RNAse_median_df <- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
n <-1
while (n < 75){
    temp_df <- data.frame(norm_RNAse[,n],norm_RNAse[,n+1],norm_RNAse[,n+2])
    Output_df <-data.frame(apply(temp_df,1,median))
    RNAse_median_df<- cbind(RNAse_median_df,Output_df)
    n <- n + 3
}
colnames(RNAse_median_df) = c(paste("frac",0:25, sep = "_"))
RNAse_median_df = RNAse_median_df[,-1]



Ctrl_median_df <- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
n <-1
while (n < 75){
    temp_df <- data.frame(norm_Ctrl[,n],norm_Ctrl[,n+1],norm_Ctrl[,n+2])
    Output_df <-data.frame(apply(temp_df,1,median))
    Ctrl_median_df<- cbind(Ctrl_median_df,Output_df)
    n <- n + 3
}
colnames(Ctrl_median_df) = c(paste("frac",0:25, sep = "_"))
Ctrl_median_df = Ctrl_median_df[,-1]



```


*works----
now by arithmetic mean ##results in RNAse_mean_df & Ctrl_mean_df
```{r}
RNAse_mean_df <- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
n <-1
while (n < 75){
    temp_df <- data.frame(norm_RNAse[,n],norm_RNAse[,n+1],norm_RNAse[,n+2])
    Output_df <-data.frame(apply(temp_df,1,mean))
    RNAse_mean_df<- cbind(RNAse_mean_df,Output_df)
    n <- n + 3
}
colnames(RNAse_mean_df) = c(paste("frac",0:25, sep = "_"))
RNAse_mean_df = RNAse_mean_df[,-1]



Ctrl_mean_df <- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
n <-1
while (n < 75){
    temp_df <- data.frame(norm_Ctrl[,n],norm_Ctrl[,n+1],norm_Ctrl[,n+2])
    Output_df <-data.frame(apply(temp_df,1,mean))
    Ctrl_mean_df<- cbind(Ctrl_mean_df,Output_df)
    n <- n + 3
}
colnames(Ctrl_mean_df) = c(paste("frac",0:25, sep = "_"))
Ctrl_mean_df = Ctrl_mean_df[,-1]
```



# Maxima detection

*works generating maxima detection testing vector exp_maxima_vec
```{r}
#test vector to look at a complex maxima detection
exp_maxima_vec<-c(1,2,3,2,1,6,5,4,2,2,3,4,3,2,5,3,2,1,3,1,4,3,2,2,1)
barplot(exp_maxima_vec)
```


*works This chunk contains maxima_loc_func a length 25 logicl vec, containing all maxima as True, and a 
Output: maxima_loc_func (x)
testing outputs:    
---exp_maxima_logic_max
---Maxima_location_vector
---exp_maxima_vec

```{r}
maxima_logic_func <-function(x,threshhold){ # x = Data_vec , threshold = % global max that is recognized as a local max
  
  threshhold_val <- max(x)*threshhold #could define a threshold 
  logic_return <-logical(length = length(x)) #logic vector 25x FALSE
  i <- 1
  while (i <= 25){
# for the first element
    if (i == 1){
      if (x[i] > x[i+1] & x[i] > threshhold_val){ 
        logic_return[i] <- TRUE
      }
#for the elemets 2-24
    }else if ( i < length(x)){
        if (x[i] > x[i+1] & x[i] > x[i-1] & x[i] > threshhold_val){ 
          logic_return[i] <- TRUE
        }
#for the last element
    }else if ( i == length(x)){
      if (x[i] > x[i-1] & x[i] > threshhold_val){ 
        logic_return[i] <- TRUE
      } 
    }
    i  <- i+1
  }
  return(logic_return) #returns the edited logic vector
  
}



```

contains dY_fac_func, input: x = Ctrl, y = Rnase, threshhols = threshhold
Output: df with 3 cols: dY_fac, prot_num, max_loc

Outputs: median_dY_fac, mean_dY_fac, lof_dY_fac 

```{r}
'RNAse_val @ Crtl_max/Ctrl_val @ Ctlr_max'

dY_fac_func <- function(x,y,threshhold){ # x = Ctrl, y = RNAse, threshhold = treshhold
#creating a 3 colum dataframe to store Output Factor, the prot num, max frac num
  factor_df <-data.frame("RNAse_factor","Prot_num","frac_num")
  factor_df[-1,]
  colnames(factor_df)<-c("RNAse_factor","Prot_num","frac_num")
  
#iterating over all the proteins 
  i <- 1
  while (i < dim(x)[1]){
    #vector for selecting the maxima
      temp_max_loc_vec <- which(maxima_logic_func(x[i,],threshhold)) 
    
  #if condition necessary for case of no maxima detected
    if (length(temp_max_loc_vec > 0)){
      
          #df for the factors of RNAse_val @ Crtl_max/Ctrl_val @ Ctlr_max
            temp_factor_df <-t(as.data.frame(y[i,][temp_max_loc_vec]/x[i,][temp_max_loc_vec])) 
          #setting the row names to eg: SPB6_HUMAN_frac_3 etc for the maxima_locations values and 
            row.names(temp_factor_df) <-c(paste(row.names(x)[i],"frac",temp_max_loc_vec[1:length(temp_max_loc_vec)],sep = "_"))
        
          #creating k as df for the protein number & l as df for the fraction number of the maxima
            k <- as.data.frame(rep(i,length(temp_max_loc_vec)))
                    row.names(k)<-row.names(temp_factor_df)
            l <- as.data.frame(temp_max_loc_vec)
                    row.names(l)<-row.names(temp_factor_df)
          #adding k and l to temp_factor_df 
            temp_factor_df <-cbind(temp_factor_df,k,l)
    
    }else{
      temp_factor_df <-as.data.frame(NA,make.names(rownames(x)[i]))
      #creating k as df for the protein number & l as df for the fraction number of the maxima
            k <- as.data.frame(rep(i,1))
                  row.names(k)<-row.names(temp_factor_df)
            l <- as.data.frame(NA)
                  row.names(l)<-row.names(temp_factor_df)
      #adding k and l to temp_factor_df 
            temp_factor_df <-cbind(temp_factor_df,k,l)
    }

    #setting col names for the temp_df = factor_df, rbind only works if colnames match
    colnames(temp_factor_df)<-colnames(factor_df)
    #saving output of each run under the last in factor_df
    factor_df <-rbind.data.frame(factor_df,temp_factor_df)
    #moving i by one to select the next row in Crtl & RNAse to compare
    i <-i+1
  }
  #removing the unwanted first row that i generated
   factor_df[-1,]
  #result of the function is returned
   return(factor_df)
}

median_dY_fac <- dY_fac_func(Ctrl_median_df,RNAse_median_df,0.2)
median_dY_fac[-1,]

mean_dY_fac <- dY_fac_func(Ctrl_mean_df,RNAse_mean_df,0.2)
mean_dY_fac[-1,]

lof_dY_fac <- dY_fac_func(Ctrl_lof_df,RNAse_lof_df,0.2)
lof_dY_fac[-1,]


#igore these for now
Ctrl_median_one <-median_dY_fac
Ctrl_median_one[,1] <- 1

Ctrl_mean_one <- mean_dY_fac
Ctrl_mean_one[,1] <- 1

Ctrl_lof_one <-lof_dY_fac
Ctrl_lof_one[,1] <- 1

```
if x < 1
1/x * frac_num 






