---
title: "Izar Code"
author: "Izar"
date: "1 5 2021"
output: html_document
---

#this code turns out two dfs that have the ratio of the difference between the maximum and minimum values and their mean in a set
# of 3 repititions in a fraction orderd by protein by fraction this will help us analyse the data nd see which
# threshhold we want to set for eliminating points of data or merely selecting points of data
# furter steps include: calculating the mean and sd of the ratios
#                       evaluating the impact of NAs
#                       selecting protein x fraction where data is significant
#                       removing insignificant data from set

Loading Data and Packages

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)

#loading data into Raw_Data dataframe
Raw_Data<- read.table("c://Data_Analysis//RDeeP_A549_NS.csv", header=TRUE, row.names=1, sep = ";")

#function for ratio of max-min to mean allows setting of univeral limit
min_max_mean_func <- function(x){
  (max(x)-min(x))/mean(x)
}
```

```{r}
'
#RNAse Factor df         
RNAse_frac_df <- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data)) #creating a dataframe to save results too

n <-2 # for RNAse n = 2 for ctrl n =1 corresponding to position in dataframe
while (n < 150){ # this will iterate trough all the fractions

    temp_df <- data.frame(Raw_Data[,n],Raw_Data[,n+2],Raw_Data[,n+4])  # a temporary df for sotring the 3 reps of each fraction
    
    Output_df <-data.frame(apply(temp_df,1,min_max_mean_func))     #the function for comparing (max-min)/mean is applied across the rows apply(...,1,..) for rows 2 for cols
    
    RNAse_frac_df <- cbind(RNAse_frac_df,Output_df)           #each run through adds a colum to RNAse_frac_df, we end with 26 cols
    
    n <- n + 6     # the counter is increased to select the next fraction
}
colnames(RNAse_frac_df) = c(paste("frac",0:25, sep = "_"))

RNAse_frac_df = RNAse_frac_df[,-1] #this code deletes the unnessecary first null colum
```

```{r}
'
#Control Factor df
ctrl_frac_df <- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
n <-1
while (n < 150){
    temp_df <- data.frame(Raw_Data[,n],Raw_Data[,n+2],Raw_Data[,n+4]) 
    Output_df <-data.frame(apply(temp_df,1,min_max_mean_func))
    ctrl_frac_df <- cbind(ctrl_frac_df,Output_df)
    n <- n + 6
}
colnames(ctrl_frac_df) = c(paste("frac",0:25, sep = "_"))

ctrl_frac_df = ctrl_frac_df[,-1] #this code deletes the unnessecary first null colum
```


Normalizing Protein data x/ntot   ##results in Norm_Data_df
```{r}

T_P_S_df <- data.frame(Total_Protein_Sum)
T_P_S_vec <-c(T_P_S_df[1,],T_P_S_df[4,],T_P_S_df[2,],T_P_S_df[5,],T_P_S_df[3,],T_P_S_df[6,])
T_P_S_vec_div_func <- function(x){
  x/T_P_S_vec
}
Norm_Data_df <- t(data.frame(apply(Raw_Data,1,T_P_S_vec_div_func)))


```

Creating seperate RNAse and Ctrl dfs    ##results in norm_RNAse & norm_Ctrl
```{r}
# Normailized RNAse only
RNAse_select_vec <- c(seq(from =2, to = 150, by = 2))
norm_RNAse <-data.frame(Norm_Data_df[,RNAse_select_vec])

#Normalized Ctrl only
Ctrl_select_vec <- seq(from =1, to = 150, by = 2)
norm_Ctrl <- data.frame(Norm_Data_df[,Ctrl_select_vec])
```

Now applying statistical
DIXON test, LOF test with DMwR::lofactor function or selfmade test
either want output df without outliers, or a outlier TRUE / FALSE matrix or a 0/1 matrix in same dim as norm dfs to get norm dfs without outliers

Trying to apply LOF/lof   ##results in NoOut_norm_RNAse_df & NoOut_norm_Ctrl_df
```{r}
library(DDoutlier)
library(dbscan)

LOF_func <-function(x){ #creating function usable in apply
  lof(x,2)
}

#issues with applying DDoutlier::LOF and dbscan::lof 
' data.frame(apply(data.frame(norm_RNAse[,1],norm_RNAse[,2],norm_RNAse[,3]),1,lof))
Error in FUN(newX[, i], ...) : x needs to be a matrix or a dist object!
 data.frame(apply(data.frame(norm_RNAse[,1],norm_RNAse[,2],norm_RNAse[,3]),1,LOF))
Error in if (k >= n || k < 1) { : missing value where TRUE/FALSE needed'

#creating empty dataframe to store results
NoOut_norm_RNAse_df <- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
'need to figure out how to save the results back into a 3680x150 df
 want to compare 3 values then make 3 colums and 3680 rows out of the resulting LOF vector
 then add them together to get a resulting df where the LOF factors coincide with the vaules
that the fractions have.
step 1 seperate the Raw Data into RNAse and Ctrl each with 3680x75 now we have rep 1,2,3 next to each other
step 2 apply(temp_vec,1,LOF_func) to a temp vec consisting of rep n,n+1,n+2
step 3 save into empty df'
n <-1
while (n < 75){
    temp_df <- data.frame(norm_RNAse[,n],norm_RNAse[,n+1],norm_RNAse[,n+2])
    Output_df <-data.frame(apply(temp_df,1,LOF_func))
    NoOut_norm_RNAse_df <- cbind(NoOut_norm_RNAse_df,Output_df)
    n <- n + 3
}
NoOut_norm_RNAse_df = NoOut_norm_RNAse_df[,-1]
colnames(NoOut_norm_RNAse_df) = c(colnames(norm_RNAse))# finish naming later


```


Removing Values based on if Outlier or not ##results in clean_RNAse_df & clean_Ctrl_df'
```{r}
#modifying the LO factor df  to remove any value above  (arbitrary) 1.5, setting all values < 1.5 = 1 and all values >1.5 = 0
data_clean_func <- function(x,z,treshhold){ # x = data to clean # z = LOF output df RNASe or Ctrl #threshhold can be played around with for signifacance of data
  treshhold_clean_func <- function(y){
    if (y >= treshhold){
      y <- 0
    }else{
      y <- 1
    }
  }
  
  binary_removal_df <- data.frame(apply(z,1,treshhold_clean_func))
  
  x*binary_removal_df
  
}
# i realized we might want to set 0 to NA before doing data cleaning think about it later
clean_RNAse_df <- data_clean_func(norm_RNAse,LOF_RNAse,1.5)
clean_RNAse_df[clean_RNAse_df == 0] <- NA
clean_Ctrl_df <- data_clean_func(norm_Ctrl,LOF_Ctrl,1.5)
clean_Ctrl_df[clean_Ctrl_df == 0] <- NA


```


mean of RNAse and Ctrl reps  ## results in clean_mean_RNAse_df & clean_mean_Ctrl_df
```{r}
# creating mean_clean_RNAse_df 3860x25, normalized and cleaned of outlieres
mean_clean_RNAse_df<- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
n<-2
while (n < 75){
    temp_df <- data.frame(clean_RNAse_df[,n],clean_RNAse_df[,n+1],clean_RNAse_df[,n+2])
    Output_df <-data.frame(apply(temp_df,1,mean))
    mean_clean_RNAse_df<- cbind(mean_clean_RNAse_df,Output_df)
    n <- n + 3
}
colnames(mean_clean_RNAse_df) = c(paste("RNAse","frac",0:25, sep = "_"))
mean_clean_RNAse_df = mean_clean_RNAse_df[,-1]


# creating mean_clean_Ctrl_df 3860x25, normalized and cleaned of outlieres
mean_clean_Ctrl_df<- data.frame(matrix(nrow = 3680, ncol=1),row.names = row.names(Raw_Data))
n<-1
while (n < 75){
    temp_df <- data.frame(clean_Ctrl_df[,n],clean_Ctrl_df[,n+1],clean_Ctrl_df[,n+2])
    Output_df <-data.frame(apply(temp_df,1,mean))
    mean_clean_Ctrl_df<- cbind(mean_clean_Ctrl_df,Output_df)
    n <- n + 3
}
colnames(mean_clean_Ctrl_df) = c(paste("Ctrl","frac",0:25, sep = "_"))
mean_clean_Ctrl_df = mean_clean_Ctrl_df[,-1]
```


Comparison tests between RNAse and Ctrl

check normality 
wilcox.test() if not normal
t.test(before, after, paired = TRUE) if normal
```{r}



```


focusing stat test on changes in fractions 19-25
check norm then decide test 
```{r}


```



